Parallel multi-objective optimization using selective operation application islands

### 2017-06-13 hpmoon-coor.tex
Revises bibliography
And eliminates duplicates reference.

\title{Parallel multi-objective optimization using selective operation application
  islands}
% New title suggestion
% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
% PABLO: Renaming again to avoid using the co-evolutionary and cooperative

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
modeling the PF by dividing it in different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. Even other types of metaheuristics, such as
the Multi-Objective Ant Colony Optimization (MOACO), can rely on
island models to divide the search space depending on the node to
achieve better results \cite{Mora13Moacos}.

>>>>

\title{Parallel multi-objective optimization using selective operation application
  islands}
% New title suggestion
% Should co-evolutionary go somewhere? Are they co-evolutionary? - jj
% PABLO: Renaming again to avoid using the co-evolutionary and
% cooperative
% Ok - JJ

@@

Giving the responsibility of different parts of the search space to
different modules, has also been explored lately by some
researchers. For example, some authors focus on the solution space
modeling the PF by dividing it in different clusters, allowing an
easily parallelizable {\em divide and conquer} approach
\citep{cheng2015adaptive}. Even other types of metaheuristics, such as
the Multi-Objective Ant Colony Optimization (MOACO), can rely on
island models to divide the search space depending on the node to
achieve better results \cite{Mora13paretobased}.
